\sys: Automated Data-Parallel Shell Processing

### 2020-04-12 pldi/draft.tex
Add new figures and table in the paper

    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--200).} 
      Three different configurations per benchmark:
      (i) distributed, focusing only on the distributed execution,
      (ii) +compile, adding \sys' pre-processing overheads, and
      (iii) +merge, adding a final merger step.
      \nv{Candidate values, based on the HW we have 2, 4, 8, 16, 32, 64. Also, maybe it makes sense to show log x-axis?}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

>>>>

    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/topn_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:topn}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/wf_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:wf}
    \end{subfigure}%
    ~
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{\detokenize{./figs/shortest_scripts_throughput_scaleup.pdf}}
        %% \caption{TODO}
        %% \label{eval:spell}
    \end{subfigure}%
    \caption{
      \textbf{Speedup achieved by \sys as a function of the level of parallelism (1--100).} 
      Three different configurations per benchmark:
      (i) parallel, focusing only on the parallel execution,
      (ii) +compile, adding \sys' pre-processing overheads, and
      (iii) \kk{Add with , without eager and split here}.
      \nv{Candidate values, based on the HW we have 2, 4, 8, 16, 32, 64. Also, maybe it makes sense to show log x-axis?}
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}
